En garde! Unguarded iteration for reversible computation in the Delay monad\thanks{Supported by organization x.}

### 2019-04-29 mpc19/paper.tex
Minor corrections.

\newcommand{\N}{\mathbb{N}}
\newcommand{\Pio}{\ensuremath{\mathsf{\Pi}^{\mathsf{o}}}} 
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Par}{\mathsf{Par}}
\newcommand{\comp}{\circ}
\newcommand{\U}{\mathcal{U}}
\newcommand{\copair}[2]{[#1,#2]}
\newcommand{\pair}[2]{\left< #1,#2 \right>}
\newcommand{\inl}{\mathsf{inl}}
\newcommand{\inr}{\mathsf{inr}}
\newcommand{\fst}{\mathsf{fst}}
\newcommand{\snd}{\mathsf{snd}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\Inv}{\mathsf{Inv}}
\newcommand{\iter}{\mathsf{iter}}
\newcommand{\mapL}[1]{#1_{\mathsf{L}}}
\newcommand{\mapR}[1]{#1_{\mathsf{R}}}

@@

Formally, the collection of types of \Pio\ constitutes the free
dagger-traced rig inverse category with recursive types. \todo{Robin: Does
  this make any sense? Also, anything to add here? Like some facts
  about \Pio, like Turing completeness.}

@@

The list of term equivalences in Figure \ref{fig:programequivs}
contains the trace axioms, displaying that the types of \Pio\ form a
traced monoidal category wrt. the additive monoidal structure
$(\Z,\oplus)$ \cite{Karvonen19}. Next we ask for
$\trace\,(\dagger\,f)$ to be the partial inverse of
$\trace\,f$. Remember that we have defined $\dagger\,(\trace\,f)$ to
be $\trace\,(\dagger \,f)$, so the axiom $\mathsf{tracePIso}$
is evidence that the trace combinator of \Pio\ is a dagger trace.
Afterwards we have two equivalences stating that $\unfold$ is the
total inverse of $\fold$. Finally,... 
\todo{Robin: a nice description of the last equivalence in Figure 3?
  Perhaps a citation too?}

It is possible to show that every term $f$ has $\dagger\,f$ as its
partial inverse, therefore proving that the types of \Pio\ possess an
inverse category structure \todo{Am I right here?}. The proof proceeds by induction on $f$.
\[
\mathsf{existsPIso} : (f : A \lr B) \to f \bullet \dagger\,f
\bullet\,f \LR f
\]

>>>>

\newcommand{\N}{\mathbb{N}}
\newcommand{\Pio}{\ensuremath{\mathsf{\Pi}^{\mathsf{o}}}} 
\newcommand{\Set}{\mathsf{Set}}
\newcommand{\Par}{\mathsf{Par}}
\newcommand{\comp}{\circ}
% \newcommand{\U}{\mathcal{U}}
\newcommand{\copair}[2]{[#1,#2]}
\newcommand{\pair}[2]{\left< #1,#2 \right>}
\newcommand{\inl}{\mathsf{inl}}
\newcommand{\inr}{\mathsf{inr}}
\newcommand{\fst}{\mathsf{fst}}
\newcommand{\snd}{\mathsf{snd}}
\newcommand{\T}{\mathsf{T}}
\newcommand{\Inv}{\mathsf{Inv}}
\newcommand{\iter}{\mathsf{iter}}
\newcommand{\mapL}[1]{#1_{\mathsf{L}}}
\newcommand{\mapR}[1]{#1_{\mathsf{R}}}

@@

Formally, the collection of types of \Pio\ correspond to those naturally
interpreted in dagger traced $\omega$-continuous rig categories (see
\cite{Karvonen19}).

@@

The list of term equivalences in Figure \ref{fig:programequivs}
contains the trace axioms, displaying that the types of \Pio\ form a
traced monoidal category wrt. the additive monoidal structure
$(\Z,\oplus)$ \cite{Karvonen19}. Next we ask for
$\trace\,(\dagger\,f)$ to be the partial inverse of
$\trace\,f$. Remember that we have defined $\dagger\,(\trace\,f)$ to
be $\trace\,(\dagger \,f)$, so the axiom $\mathsf{tracePIso}$
is evidence that the trace combinator of \Pio\ is a dagger trace.
Afterwards we have two equivalences stating that $\unfold$ is the
total inverse of $\fold$.

It is possible to show that every term $f$ has $\dagger\,f$ as its partial
inverse, and since the final equivalence of Figure~\ref{fig:programequivs} is
equivalent to stating that partial inverses are unique~\cite{Kastl79}, it
follows that the types and terms of \Pio\ form an inverse category. The proof
proceeds by induction on $f$.
\[
\mathsf{existsPIso} : (f : A \lr B) \to f \bullet \dagger\,f
\bullet\,f \LR f
\]
